Information Closure Theory of Consciousness

### 2019-09-20 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

	\begin{abstract}
		Neural systems process information through different levels of organisation in a hierarchical manner. Information at lower levels is finer-grained and can be coarse-grained for higher level computation. However, one is aware of information processed only at specific levels. Theorists have addressed this issue. For example, the intermediate level theory of consciousness suggests that the intermediate level seems to be privileged with respect to consciousness. It is true that we do not experience information processed by individual neurons which is always highly stochastic noisy. In addition, we have no conscious experience from interpersonal activities despite massive interactions among individuals. Instead, neurophysiological evidence has been showing that conscious experience tends to co-vary with information encoded in coarse-grained neural states such as neural population codes. We argue that the content of consciousness is determined by neural variables that obey informational closure and that other brain processes remain unconscious. Out theory based on concise assumptions and propose quantitative definitions using information theorem for both conscious content and conscious level.

@@

% ============================================================================ %
    \newpage
    \section*{Not decided terminology}
        \begin{ants}
            @ information * in the NTIC process
            @ Full and short name of this theory
            @ core "?" (entity) for conscious content 
            @ our theory? framework? proposal? 
            @ system? process?
            @ variable? node? element? member?
            @ TODO:
                @@ Change coarse-graining function to "aggregation function"
            @ Decided
                @@ "form" NTIC
            @ Replacement
                @ correlate -> ?
                @ information processing -> ?
                @ achieve -> form
        \end{ants}

% ============================================================================ %
    \newpage
    \section*{Discussion points}
        \begin{ants}
            @ I can understand that an NTIC process must be coarse-graining of the "full process" (Environment + NTIC or we say {E, Y}). But I am still thinking is this the same as my original idea that variables forming the NTIC process are coarse-grained from microscopic variables? This is very critical to how we present this paper.

        \end{ants}

@@

		It seems to be true that we are not consciously accessing information processed at every scale in the neural system. There are both more microscopic and more macroscopic levels than the level corresponding to the conscious contents. On the one hand, dynamics of individual neurons are stochastic \citep{Goldwyn2011, White2000}. However, what we are aware of in our conscious mind shows astonishing stability and robustness against the ubiquitous noise in the neural system \citep{mathis1995computational}. In addition, some parts of the neural system contribute very little to conscious experience (the cerebellum for example \citep{lemon2010life}), also suggesting that conscious contents do not have one-to-one mapping to the entire state of the neural system. On the other hand, human conscious experience is more detailed than just a simple (e.g. binary) process can represent, suggesting that the state space of conscious experience is much larger than what a single overly coarse-grained binary variable can represent. These facts suggest that conscious processes are scale dependent. We refer to this notion as \textbf{the scale problem of consciousness} (Fig.~\ref{fig:scaleproblem}).

		%% our argument
		In this article, we propose a new information-based theory of consciousness, called \ac{OurTheory}. We argue that every process with a high degree of not-trivial information closure (NTIC) has consciousness. This means that the state of such a process corresponds one-to-one to conscious content.\footnote{In the following IC stands for "informational closure" or "informationally closed" and NTIC stands for "non-trivial informational closure" or "non-trivially informationally closed".}. We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC. (for the level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).

		In the following, we first introduce non-trivial informational closure and its importance to information processing for human scale agents (Sec.\ref{sec:Non-trivial informational closure}). We next argue that through coarse-graining the neural system can form a high degree of NTIC at a specific coarse-grained level (Sec.\ref{sec:Neural coarse-graining}). In the Sec.\ref{sec:OurTheory}, we propose our theory: \acf{OurTheory}. We also illustrate how \ac{OurTheory} can parsimoniously explain empirical findings from previous consciousness studies (Sec.\ref{sec:Conscious versus Unconscious Processing}) and reconcile several current major theories of consciousness (Sec.\ref{sec:Comparison with other theories}). Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications from this theory to the current consciousness science (Sec.\ref{sec:Limitation and Future work}).

@@

				\begin{figure}
					\includegraphics[width=\textwidth]{WritingMaterials/Fig_SystemAndEnv/SystemAndEnv_2.pdf}
					\caption{The dependencies between a system and its environment.} % Figure adapted from \cite{BERTSCHINGER.2006}
					\label{fig:SystemAndEnv}
				\end{figure}
				\todo{Modify this figure}

@@

			\noindent
			This implies the system contains in itself all the information about its own future and the self-predictive information is gained from the information about the environment. Therefore, to form NTIC, the system can internalise and synchronise the dynamics of the environment, i.e. modelling the environment. Furthermore, having high degrees of NTIC entails having high predictive power about the environment. This gives biological agents a great functional and evolutionary advantage.

@@

		%% stochasticity at microscopic levels
		Despite the evolutionary advantage of having NTIC processes in a system, however, to create NTIC with a highly stochastic process is challenging. NTIC requires the predictability of the system state and is therefore impeded by noise in the system. Information processing at the microscopic levels (the cellular levels) in neural systems suffer from multiple environmental noise sources throughout, including sensory, cellular, electrical, and synaptic noises. For example, neurons have large trial-to-trial variability at the cellular level, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.

        % 		Furthermore, environmental information is always only partially observable to individual sensors and neurons which only receive little amount of information from the environment. Therefore, information about the environment state at the cellular level is difficult to represent at the cellular level. It is implausible to construct NTIC processes at microscopic levels.

        %% Our argument
		However, we argue that, neural systems can form NTIC at certain macroscopic levels through coarse-graining microscopic neural states. Coarse-graining refers to many-to-one functions which aggregate microscopic states to a macroscopic state. In other words, a number of different micro-states realise the same value of the macro-variable \citep{price2007causation}. Neural systems, therefore, can form more stable and deterministic state transitions and be more capable of forming NTIC processes at certain coarse-grained macroscopic levels.

		Indeed, empirical evidence has been showing that coarse-graining is a common coding strategy against ubiquitous stochasticity at microscopic levels of the the neural system. For instance, the inter-spike intervals of individual neurons are stochastic. This implies that states of individual neurons are incapable of encoding and representing stable information. However, the spiking rate, i.e. the average spike counts in a given time interval, shows astonishing stability and robustness against noise causing the variation of inter-spike intervals. Using this temporal coarse-graining strategy, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}, individual neurons can encode stimulus intensity by increasing or decreasing firing rate \citep{kandel2000principles}. \citep{stein2005neuronal}. The robustness of the rate coding is direct consequence of the many to one map used.

		% population code
		Population coding is another example of encoding information through coarse-graining in neural systems. In this coding scheme, information is encoded by activation patterns of a set of neurons (a neuron population). To reduce the influence noise on scholastic state transitions of individual neurons, many states for a neuron population map to the same information content. Therefore, stable representation can be formed through coarse-graining a high dimensional state space of a neuron population to a low dimensional state space of encoded contents \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}. Therefore, individual neuron states (the microscopic level) are not informative about the encoded contents at the population level (the macroscopic level). Instead, coarse-grained variables are better entities to encode information and allow the neural system to ignore noisy causal interaction at the fine-grained level of description \citep{Woodward2007-WOOCWA}.

        The two examples show that coding schemes through coarse-graining could provides a stochastic system, e.g. the neural system, to form more stable and deterministic macroscopic processes to encode and process information reliably. We argue that through coarse-graining the neural systems is able to form NTIC processes at macroscopic levels. Based on this argument, we proposes our theory of consciousness in the next section.

@@

% ============================================================================ %
% Boundary problem 1: Add another NTIC process
% 1. Ignore it / maybe next paper
% 2. Acknowledge the problem but we don't have solution now
% 3. Write down our comment

% Micro/Macro and Environment point of views
%   Whether a process can be a part of the environment
% ============================================================================ %

% ============================================================================ %
%               A neural coarse graining theory of consciousness               %
% ============================================================================ %
	\section{A neural coarse graining theory of consciousness}\label{sec:OurTheory}

        In this section, we propose a new theoretical framework of consciousness: \acf{OurTheory}. We also discuss the implications of \ac{OurTheory} in Sec.~\ref{sec:cl}, \ref{sec:cc}, and \ref{sec:reconcile}.

        We argue that the existence of an NTIC process within a system is sufficient for information processing to be conscious.

        In what follows, we will first establish three assumptions on which this theory depends. Then, we will develop the propositions in detail.

@@

		\begin{equation}
			\label{eq:ICchain}
			\begin{aligned}
		    & I(Y_{t+1};X_t|Y_{t})=0 & \implies & I(Y_{t+1};S_t|Y_{t})=0 \\
		    & {} & \implies & I(Y_{t+1};E_t|Y_{t})=0
			\end{aligned}
		\end{equation}

@@

            First, to form high level of NTIC, one can increase the mutual information $I(Y_{t+1};Y_{t})$ between the current internal state $Y_t$ and the future internal state $Y_{t+1}$. In other words, conscious levels are associated with the degree of self-predictive information. This mutual information term can be further decomposed to two information entropy quantities:

@@

            This implies that a high NTIC process should have a rich dynamic and concurrently maintain self-productiveness overtime. Another implication is that a complex systems can potentially reach higher levels of consciousness due to a larger information capacity to achieve higher mutual information. This outcome is consistent with a common intuition that conscious levels are associated with the degrees of complexity of systems.

    	    Second, one can minimise the conditional mutual information $I(Y_{t+1};Y_{t}|E_{t})$ to increase the level of NTIC. This quantity suggests that conscious level increases with the level of information about the environment state $E_t$ that the NTIC process encodes in its own state $Y_t$. An important implication is that a NTIC possessed by an agent which interacts with and adapts to a complex environment should have a higher level of NTIC than one possessed by another agent which lives and adapts to a simple environment. In other words, the environmental complexity is associated with conscious levels of NTIC processes.

    	    %% not monotonic
    		It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining. We saw above that not coarse-graining enough and therefore considering processes that are too microscopic leads to low values of NTIC. However, if the macroscopic variable is overly coarse-grained the system states can result in low degrees of NTIC. For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus looses the self and environmental predictive power. \ac{OurTheory}, therefore, argues that only processes at a certain level of coarse-graining in the neural system can reach high level of NTIC (Fig.~\ref{fig:LevelOfConsciousness}). As a result, there exists a certain level of coarse-graining which has a maximal conscious level within the neural system.

@@

            \ideaBox{About Human Scale}
            Finally, which coarse-grained level can form high NTIC? 
            agent-scale operation
            At the physical scale which human being interact with, the environmental dynamics is nearly deterministic following the laws of classical physics. It gives agents interact at this physical scale great advantages if the agents can build NTIC process internally. Therefore, to coarse-grain microscopic states is necessary

            %% Link to consciousness
            At the physical scale which human beings live in, the environmental dynamics is nearly deterministic following the laws of classical physics. This suggests that information in the environment is nearly closed at the right spatio-temporal scale. Therefore, this gives agents living at this physical scale great advantages if the agents form an NTIC process internally. Therefore, coarse-graining becomes necessary to map microscopic sensory and neuronal states into macroscopic NTIC process.

		\subsection{Conscious Contents Corresponding to States of a NTIC process}\label{sec:cc}
    	    % richness 
    		\ac{OurTheory} proposes that conscious contents correspond to states of NTIC processes (Eq.~\ref{eq:cContent}). This implies that the size of the state space of a NTIC process is associated with the richness of conscious contents that the process can potentially have. Therefore, a complex NTIC process with a high dimensional state space can have richer conscious experience than a simple NTIC process can have. This outcome is consistent with a the intuition that the richness of conscious contents is associated with the complexity of a system.

@@

    		Importantly, NTIC processes encodes environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics. This implication fit well with mental simulation theory of consciousness, predictive processing perspective of consciousness, and information generation theory of consciousness \needref{need three}. Note that \ac{OurTheory} doesn't assume that generative models are necessary. The implication a natural consequence based on our proposition.

            Finally, due to a coarse-graining is a many to one map from microscopic to macroscopic scales, our theory implies multiple realisation thesis of consciousness\needref{multiple realisation} which suggests different physical implementation can map to the same conscious experience.

		% ---------------------------------------------------------------------------- %
        %             Reconciling the levels and contents of consciousness             %
        % ---------------------------------------------------------------------------- %
	    \subsection{Reconciling the levels and contents of consciousness}\label{sec:reconcile}
    	    Segregation of conscious levels and conscious contents raises a debate \citep{bayne2016there, Fazekas2016}. In \ac{OurTheory} conscious levels and conscious contents are just two different properties of NTIC processes, and, therefore, naturally reconciles the two aspects of consciousness. To form high NTIC, a NTIC process needs to have a large and potentially high state space which guarantees rich and high dimensional information in conscious contents. Therefore, this framework well integrates the two key but debated concepts in consciousness research

    	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that the the size of the state space and information entropy $H(Y)$ of a NTIC process are associated with both conscious levels and conscious contents. To reach high NTIC, a process needs to have a large state space and high information entropy which guarantee rich conscious contents and also the capacity of predictive information of the system (Eq.~\ref{eq:nticObjective}).
    	    \ac{OurTheory} therefore explains why in normal physiological states conscious levels and conscious contents are positively correlated \citep{laureys2005neural}. This implication is also in line with the intuition in which consciousness is often associated with complex systems.

@@

% ============================================================================ %
%                    Conscious versus Unconscious Processing                   %
% ============================================================================ %
	\section{Conscious versus Unconscious Processing}\label{sec:Conscious versus Unconscious Processing}
	    In this section, we show how our theory can make predictions about what processes are conscious and what are unconscious.

@@

        % ---------------------------------------------------------------------------- %
        %                            Unconscious Processing                            %
        % ---------------------------------------------------------------------------- %
        \subsection{Unconscious Processing}
            \ac{OurTheory} proposes that NTIC is sufficient for a process to be conscious. Based on the definition of NTIC, we highlights two scenarios which lead low NTIC so that a process is unconscious. We additionally highlight the level of coarse-graining.
            \ideaCallout{Need rewording}

            % ============================================================================ %
            %                                 Fail to be IC                                %
            % ============================================================================ %
            \subsubsection*{Fail to Form Informational Closure}
                A process is not informationally closed leads to low levels of NTIC (Eq.~\ref{eq:nticObjective2}) and results in low or no consciousness. In this case, the current states of a process are largely depends on its environment states (see Fig.~\ref{fig:reflexive}) but little influenced by its past states. Reflexive behaviours \citep{casali2013theoretically} can be considered a classical example in this scenario. \ac{OurTheory} naturally explains why reflexive behaviours always do not involve voluntary conscious controls and operate unconsciously.

             	% reflexive behaviour
        		\begin{figure}[H]
        			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
        			\caption{
        			    Reflexive behaviours happen between a process $Y$ and its environment $E$ which $Y$ interact with. The red nodes and arrows represent the major information flow in reflexive reactions. The internal state of the process $Y_t$ is largely dependent on the environment state $E_{t-1}$ but less on its past state $Y_{t-1}$. Therefore, the process $Y$ is not informational closed. In consequence, $Y$ is unable to form high NTIC and, therefore, to have high conscious levels.
        			    }
        			\label{fig:reflexive}
        		\end{figure}

        		The same principle can be applied to blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedure memory \citep{doyon2009contributions, ashby2010cortical} which are often considered as unconscious processes. Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements without having any conscious perception about visual stimuli. We argue that action outputs of blindsight can be directly guided by sensory inputs through stimulus-response maps. The neural circuits are not informationally closed and, therefore, unconscious. Similarly, for procedure memory, the state transitions of action controls largely depends on the concurrent environmental states. This prevents the internal processes of procedure memory from informational closure and being conscious.

                % In the neural system, this type of processes, for perception, shows the property that the perceptual processing mainly passively responds to the sensory inputs. For actions, this type of processes only produces "reflective-like" behaviours. Reflexive behaviours are commonly considered as automatic and non-conscious behavioural controls \citep{casali2013theoretically}\needref{More referene}. We argue that information carried by this type of processes is unconscious due to its failure of achieving high NTIC, i.e., the first condition.

                % The same principle can be applied to blindsight and procedure memory \needref{blindsight} which are often considered as unconscious processing. Blindsight patients are able to track objects, avoid obstacles, and make above chance-level judgements without having any conscious perception about visual stimuli. We believe that these behaviours can be guided by direct stimulus-response mappings ($S\rightarrow{}R$). However, the direct $S\rightarrow{}R$ mappings also lead to non-NTIC neural processes  and, therefore, are unconscious. Similarly, in the case of procedure memory, processes always rely on both the current environmental and system states to determine the next state of the processes\needref{Do I need ref??}. The information flow from the environment to the system is crucial to guide the state transition of procedural memory. Therefore, information processing of procedural memory also fails to form high NTIC and remain unconscious.

        %          This type of processing is similar to the model-free policy-based agents in the reinforcement learning framework. The agent learns a policy $\pi$ which directly maps sensor values $S$ to output action $A$.
        % 		\begin{equation}
        % 			\label{eq:PolicyBasedAgent}
        % 			\begin{aligned}
        % 			    \pi(A | S)=\operatorname{Pr}\left(A_{t}=a | S_{t}=s\right)
        % 			\end{aligned}
        % 		\end{equation}

                \ac{OurTheory} explains why the patients with visual apperceptive agnosia \citep{james2003ventral} can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}. The online information from the visual inputs can be used to perform  functional actions without complete conscious perception of the visual targets.

                % Our theory also explains why unconscious processes in this category often fail when a long delay periods is introduced in the tasks. Without self-predictive information in NTIC, the policies of motor outputs largely depends on the present environmental and sensory states implying that this type of processes often can only work online. With a long, sensory information is unable to guide the delayed motor outputs and leads to failure consequences.

        		\ideaCallout{Mayeb can put in theory part}
        		An implication from \ac{OurTheory} is that a pure feedforward network is incapable to be conscious due to a lack of any form of memory. Without memory, the network current states are entirely driven by network current inputs without any influence from its past states and, therefore, is incapable to be informationally closed. In contrast, a network with recurrent loops could keep information about its states. This forms an information channel between the past and the future states of the network and, thus, makes the network becomes capable of being informationally closed. This result coincides with theories of consciousness emphasising the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.

@@

	\section*{Funding}

	\section*{Acknowledgements}

>>>>

	\begin{abstract}
		Information processing in neural systems can be described and analysed at multiple spatiotemporal scales. Generally, information at lower levels is more fine-grained and can be coarse-grained in higher levels. However, information processed only at specific levels seems to be available for conscious awareness. We do not have direct experience of information available at the level of individual neurons, which is noisy and highly stochastic. Neither do we have experience of more macro-level interactions such as interpersonal communications. Neurophysiological evidence suggests that conscious experiences co-vary with information encoded in coarse-grained neural states such as the firing pattern of a population of neurons. In this article, we assume that conscious experience is confined due to informational closure from conscious processing to other coarse-grained levels. From this and three additional assumptions, we propose a new computational theory of consciousness: \ac{OurTheory}. \ac{OurTheory} proposes new quantitative definitions of both conscious content and conscious level. With the parsimonious assumptions and simple propositions, \ac{OurTheory} provides explanations and predictions of phenomena associated with consciousness. The implications of \ac{OurTheory} naturally reconciles issues in many existing theories of consciousness and provides explanations for many of our intuitions about consciousness. Most importantly, \ac{OurTheory} indicates that information is the common language bridging consciousness and physical reality.

@@

%         \end{ants}

@@

		It seems to be true that we are not consciously accessing information processed at every scale in the neural system. There are both more microscopic and more macroscopic levels than the level corresponding to the conscious contents. On the one hand, dynamics of individual neurons are stochastic \citep{Goldwyn2011, White2000}. However, what we are aware of in our conscious mind shows astonishing stability and robustness against the ubiquitous noise in the neural system \citep{mathis1995computational}. In addition, some parts of the neural system contribute very little to conscious experience (the cerebellum for example \citep{lemon2010life}), also suggesting that conscious contents do not have one-to-one mapping to the entire state of the neural system. On the other hand, human conscious experience is more detailed than just a simple (e.g. binary) process can represent, suggesting that the state space of conscious experience is much larger than what a single overly coarse-grained binary variable can represent. These facts suggest that conscious processes occur at a particular scale. We currently lack a theory to identify the scale which conscious processes correspond to. We refer to this notion as \textbf{the scale problem of consciousness} (Fig.~\ref{fig:scaleproblem}).

		%% our argument
		In this article, we propose a new information-based theory of consciousness, called \ac{OurTheory}. We argue that every process with a high degree of non-trivial information closure (NTIC) has consciousness. This means that the state of such a process corresponds one-to-one to conscious content.\footnote{In the following IC stands for "informational closure" or "informationally closed" and NTIC stands for "non-trivial informational closure" or "non-trivially informationally closed".}. We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC. (for the level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).

		In the following, we first introduce non-trivial informational closure and argue for its importance to information processing for human scale agents (Sec.\ref{sec:Non-trivial informational closure}). We next argue that through coarse-graining the neural system can form a high degree of NTIC at a specific coarse-grained level (Sec.\ref{sec:Neural coarse-graining}). In the Sec.\ref{sec:OurTheory}, we propose our theory: \acf{OurTheory}. We also illustrate how \ac{OurTheory} can parsimoniously explain empirical findings from previous consciousness studies (Sec.\ref{sec:Conscious versus Unconscious Processing}) and reconcile several current major theories of consciousness (Sec.\ref{sec:Comparison with other theories}). Finally, we discuss the current theoretical and empirical limitations of \ac{OurTheory} and propose the implications from \ac{OurTheory} to the current consciousness science (Sec.\ref{sec:Limitation and Future work}).

@@

				\begin{figure}
					\includegraphics[width=\textwidth]{WritingMaterials/Fig_SystemAndEnv/SystemAndEnv_2.pdf}
					\caption{The dependencies between a system and its environment.} % Figure adapted from \cite{BERTSCHINGER.2006}
					\label{fig:SystemAndEnv}
				\end{figure}

@@

			\noindent
			This implies the system contains in itself all the information about its own future and the self-predictive information is gained from the information about the environment. Therefore, to form NTIC, the system can internalise and synchronise with the dynamics of the environment, i.e. modelling the environment. Furthermore, having high degrees of NTIC entails having high predictive power about the environment. This gives biological agents a great functional and evolutionary advantage.

@@

		%% stochasticity at microscopic levels
		Despite evolutionary advantage of having NTIC processes in a system, however, the formation of NTIC witha  highly stochastic process is challenging. NTIC requires the predictability of the system state and is therefore impeded by noise in the system. Information processing at the microscopic levels (the cellular levels) in neural systems suffer from multiple environmental noise sources such as sensor, cellular, electrical, and synaptic noises. For example, neurons exhibit large trial-to-trial variability at the cellular level, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.

        %% Our argument
		However, we argue that, neural systems can form NTIC at certain macroscopic levels through coarse-graining of microscopic neural states. Coarse-graining refers to many-to-one functions which aggregate microscopic states to a macroscopic state. In other words, a number of different micro-states correspond to the same value of the macro-variable \citep{price2007causation}. Neural systems, therefore, can form more stable and deterministic state transitions and be more capable of forming NTIC processes at certain coarse-grained macroscopic levels.

		Indeed, empirical evidence suggests that coarse-graining is a common coding strategy to establish robustness against noise at microscopic levels of the the neural system. For instance, the inter-spike intervals of individual neurons are stochastic. This implies that the state of individual neurons cannot be used for encoding and representing stable information. However, the firing rate, i.e. the average spike counts over a given time interval, is more stable and robust against noise such as the variability in inter-spike intervals. Using this temporal coarse-graining strategy, known as the rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}, neurons can encode stimulus intensity by increasing or decreasing the firing rate \citep{kandel2000principles}. \citep{stein2005neuronal}. The robustness of the rate coding is a direct consequence of the many to one mapping (i.e., coarse-graining).

		% population code
		Population coding is another example of encoding information through coarse-graining in neural systems. In this coding scheme, information is encoded by activation patterns of a set of neurons (a neuron population). In the population coding scheme, many states for a neuron population map to the same information content, thereby reducing the influence of noise in individual neurons. That is, stable representations can be formed through coarse-graining a high dimensional state space of a neuron population to a low dimensional state space of encoded contents \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}. Therefore, individual neuron states (the microscopic level) are not informative about the encoded contents at the population level (the macroscopic level). Instead, coarse-grained variables are better substrates for stably encoding information and allow the neural system to ignore noisy interactions at the fine-grained level \citep{Woodward2007-WOOCWA}.

        These two examples show that the known coding schemes can be viewed as coarse-graining, and provide stochastic neural systems with the ability to form more stable and deterministic macroscopic processes for encoding and processing information reliably. We argue that through coarse-graining the neural systems is able to form NTIC processes at macroscopic levels. Based on the merit of coarse-graining in neural systems, We propose a theory of consciousness in the next section.

@@

% ============================================================================ %
%               A neural coarse graining theory of consciousness               %
% ============================================================================ %
	\section{\acf{OurTheory}}\label{sec:OurTheory}

        In this section, we propose a new theoretical framework of consciousness: \acf{OurTheory}.  In \ac{OurTheory}, we claim that being NTIC is sufficient for a process to be conscious. The implications of \ac{OurTheory} will be discussed in Sec.~\ref{sec:cl}, \ref{sec:cc}, and \ref{sec:reconcile}. In what follows, we will first establish four assumptions on which \ac{OurTheory} depends, and then develop the specific propositions of \ac{OurTheory} in detail.

@@

            \needhelp{@Martin, if you think it's better to have a proof for this and if you don't mind, you can help me to write the proof here or create an appendix section and put it there. If you have no time, I can also do this.}
		\begin{equation}
			\label{eq:ICchain}
			\begin{aligned}
		    & I(Y_{t+1};X_t|Y_{t})=0 & \implies & I(Y_{t+1};S_t|Y_{t})=0 \\
		    & {} & \implies & I(Y_{t+1};E_t|Y_{t})=0
			\end{aligned}
		\end{equation}

@@

            First, to form a high level of NTIC, one can increase the mutual information $I(Y_{t+1};Y_{t})$ between the current internal state $Y_t$ and the future internal state $Y_{t+1}$. In other words, conscious levels are associated with the degree of self-predictive information. This mutual information term can be further decomposed to two information entropy quantities:

@@

            This implies that a highly NTIC process must have rich dynamics with self-predictability over time. Another implication is that complex systems can potentially attain a higher level of consciousness due to the larger information capacity needed to attain high mutual information. This outcome is consistent with the common intuition that conscious levels are associated with the degree of complexity of the system.

    	    Second, one can minimise the conditional mutual information $I(Y_{t+1};Y_{t}|E_{t})$ to increase the level of NTIC. This quantity suggests that conscious level increases with the amount of information about the environment state $E_t$ that the NTIC process encodes in its own state $Y_t$. An important implication is that agents interacting with a complex environment have the chance to build a higher level of NTIC within their systems than those living in a simple environment. In other words, the level of consciousness is constrained by environmental complexity.

    	    %% not monotonic
    		It is important to note that NTIC can be a non-monotonic function of the scale of coarse-graining. We saw above that not sufficiently coarse-grained variables have low values of NTIC. On the other hand, overly coarse-grained macroscopic variables  also result in low values of NTIC. For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have any information capacity and thus cannot have high mutual information across time steps.  Therefor, only processes at a certain level of coarse-graining in the neural system can form a high degree of NTIC (Fig.~\ref{fig:LevelOfConsciousness}). \ac{OurTheory} indicates that consciousness occurs at the intermediate level of coarse-graining where the maximal NTIC is formed within the neural system.

@@

            % Finally, which coarse-grained level can form high NTIC? 
            % agent-scale operation
            % At the physical scale which human being interact with, the environmental dynamics is nearly deterministic following the laws of classical physics. It gives agents interact at this physical scale great advantages if the agents can build NTIC process internally. Therefore, to coarse-grain microscopic states is necessary

            % %% Link to consciousness
            % At the physical scale which human beings live in, the environmental dynamics is nearly deterministic following the laws of classical physics. This suggests that information in the environment is nearly closed at the right spatio-temporal scale. Therefore, this gives agents living at this physical scale great advantages if the agents form an NTIC process internally. Therefore, coarse-graining becomes necessary to map microscopic sensory and neuronal states into macroscopic NTIC process.

		\subsection{Conscious Contents Corresponding to States of a NTIC process}\label{sec:cc}
    	    % richness 
    		\ac{OurTheory} proposes that conscious contents correspond to the states of NTIC processes (Eq.~\ref{eq:cContent}). This implies that the size of the state space of an NTIC process is associated with the richness of conscious contents that the process can potentially have. Therefore, a complex NTIC process with a high dimensional state space can have richer conscious experience than a simple NTIC process can have. This outcome is consistent with the intuition that the richness of conscious contents is associated with the complexity of a system.

@@

    		Importantly, NTIC processes encodes environmental information in its state. This suggests that a NTIC process can be considered as a process that simulates the environmental dynamics. This implication fit well with some other theories of consciousness (for example, world simulation metaphor ~\citep{revonsuo2006inner}). Note that \ac{OurTheory} doesn't assume that generative models are necessary for consciousness. The implication a natural consequence based on our proposition.

            Finally, a coarse-graining is a many to one map from microscopic to macroscopic states and \ac{OurTheory} proposes that conscious contents $C_{t}^{Content}$ is the state of the NTIC process $Y_t$. Therefore, \ac{OurTheory} implies multiple realisation thesis of consciousness \citep{putnam1967psychological,bechtel1999multiple} which suggests that different physical implementations could map to the same conscious experience.

		% ---------------------------------------------------------------------------- %
        %             Reconciling the levels and contents of consciousness             %
        % ---------------------------------------------------------------------------- %
	    \subsection{Reconciling the levels and contents of consciousness}\label{sec:reconcile}
    	    While it is useful to distinguish the notion of the  levels and contents of consciousness, whether they can be clearly dissociated has been a matter of debate \citep{bayne2016there, Fazekas2016}. In \ac{OurTheory}, conscious levels and conscious contents are just two different properties of NTIC processes, and, therefore, naturally reconciles the two aspects of consciousness. In an NTIC process with a large state space, conscious contents consist of rich and high dimensional information. Therefore, this framework integrates the levels and the contents of consciousness in a coherent fashion by providing explicit formal definitions of the two notions.

    	    According to Sec.~\ref{sec:cl} and Sec.~\ref{sec:cc}, an important implication from \ac{OurTheory} is that both conscious levels and conscious contents are associated with the entropy $H(Y)$ of an NTIC process, and therefore the size of the state space. To form a high degree of NTIC for rich conscious contents, the process needs to have a large state space and also the capacity of predictive information   (Eq.~\ref{eq:nticObjective}).
    	    \ac{OurTheory} therefore explains why in normal physiological states conscious levels and conscious contents are positively correlated \citep{laureys2005neural}. This implication is also in line with the intuition in which consciousness is often associated with complex systems.

@@

    % ============================================================================ %
    %                    Conscious versus Unconscious Processing                   %
    % ============================================================================ %
	\section{Conscious versus Unconscious Processing}\label{sec:Conscious versus Unconscious Processing}
	    In this section, we show how \ac{OurTheory} can make predictions about what processes are conscious and what are unconscious. \ac{OurTheory} is constructed using information theory. Therefore, \ac{OurTheory} can provide predictions based on the mathematical definitions. In the end of this section, we discuss a critical implication of \ac{OurTheory} for neuroscience research on consciousness.

@@

        % ---------------------------------------------------------------------------- %
        %                            Unconscious Processing                            %
        % ---------------------------------------------------------------------------- %
        \subsection{Unconscious Processing}
            In this section, we highlight two scenarios in which the degree of NTIC is rendered low for a process, and thereby making the process unconscious.

            \subsubsection*{Informational is not Closed}\label{sec:reflexive}
                If a process is not informationally closed, the degree of NTIC is low (Eq.~\ref{eq:nticObjective2}) resulting in low or no consciousness. In such cases, the current state of a process depends primarily on the environment state (see Fig.~\ref{fig:reflexive}), but receives little influence from its past state. Reflexive behaviours \citep{casali2013theoretically} can be considered an example of this scenario. In \ac{OurTheory}, if we can view reflexive behaviours as situations in which the internal state $Y_t$, which triggers reflexive action, is determined by the environment state $E_{t-1}$ overruling the influences from its own past $Y_{t-1}$.  Such interpretation of reflexive behaviour from the viewpoint of \ac{OurTheory} naturally explains why reflexes do not involve conscious experience of external stimuli.

             	% reflexive behaviour
        		\begin{figure}[H]
        			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
        			\caption{
        			    A diagram depicting the information flow in reflexive behaviours (shown by the red nodes and arrows) happening through the interaction between a process $Y$ and its environment $E$. In such situations, the internal state $Y_t$ is mostly dependent on the environment state $E_{t-1}$ but less on its past state $Y_{t-1}$. Therefore, the process $Y$ is not informational closed. As a  consequence, $Y$ is unable to form high NTIC and, therefore, remain unconscious. 
        			    }
        			\label{fig:reflexive}
        		\end{figure}

        		The same principle can be applied to interpret blindsight \citep{humphrey1999history, humphrey1974vision, Humphrey1970} and procedural memory \citep{doyon2009contributions, ashby2010cortical} which are often considered as unconscious processes. Blindsight patients are able to track objects, avoid obstacles, and make above chance-level visual judgements without having any conscious perception about visual stimuli. We argue that action outputs of blindsight can be directly guided by sensory inputs through stimulus-response maps. The neural circuits are not informationally closed and, therefore, unconscious. Similarly, for procedural memory, the state transitions of action controls largely depends on the concurrent environmental states. This prevents the internal processes of procedure memory from informational closure and being conscious. \ac{OurTheory} also offer an interpretation as to why patients with visual apperceptive agnosia \citep{james2003ventral} can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}.

        		\ideaCallout{Mayeb can put in theory part}
        		As we have seen in the examples above, a crucial implication of \ac{OurTheory} is that a pure feedforward network cannot produce consciousness because NTIC requires a form of memory $I(Y_{t+1};Y_{t})$. Without memory, a network's current state is entirely driven by the input the network receives from the environment without any influence from its own past states. Therefore, such a network is incapable of forming an NTIC. In contrast, a network with recurrent loops can maintain information about its own past states. This forms an information channel between the past and the future states of the network and, thus, makes the network capable of being informationally closed. This result coincides with theories of consciousness emphasising the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.

@@

	\section*{Funding}
        \needhelp{@Ryota, could you help me with this part?}
	\section*{Acknowledgements}
